---
title: "Assignment 5 - Meta-analysis of pitch in schizophrenia"
author: "Riccardo Fusaroli"
date: "3/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Building on the shoulders of giants: meta-analysis

## Questions to be answered
```{r}
#------ Libraries ------
library(pacman)

p_load(metafor)

setwd(getwd())

#------ load data ------
#Alberto's data
data = read.csv('Data.csv', sep = ";")
#Assignment 3 data
data_3 = read.csv('full_df.csv')
data_3 = data_3[,1:12] #cut unnecessary variables

```



1. What is the current evidence for distinctive patterns of pitch mean and pitch sd in schizophrenia? Report how many papers report quantitative estimates, your method to analyze them, the estimated effect size of the difference (mean effect size and standard error for pitch mean, same for pitch sd) and forest plots representing it. 

N.B. we focus on pitch mean and pitch standard deviation.
 . first try using lmer (to connect to what you know of mixed effects models)
 . then use rma() (to get some juicy additional statistics)

- Build a forest plot of the results (forest(model))
```{r}
#Calculate standardized effect size for mean and sd
escalc_mean = escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeContros, m1i=PitchMeanSchizo, m2i=PitchMeanControls, sd1i=PitchMeanSchizoSD, sd2i=PitchMeanControlsSD, data = data)

escalc_sd = escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeContros, m1i=PitchSDSchizo, m2i=PitchSDControls, sd1i=PitchSDSchizoSD, sd2i=PitchSDControlsSD, data = data)

#Make models
m_mean = rma(yi,vi, data= escalc_mean, slab = Article)
m_sd = rma(yi,vi, data= escalc_sd, slab = Article)

#Make forest plot
forest(m_mean)
forest(m_sd)

#Make summary of models
summary(m_mean)
summary(m_sd)


```


2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots.

- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?

- Now look at the output of rma() and check tau and I2

```{r}
#------ Make the row containing our study ------
#Sample size
ss_control = length(unique(data_3$ID[data_3$Diagnosis == 0]))
ss_schizo = length(unique(data_3$ID[data_3$Diagnosis == 1]))

#Mean pitch
m_control = mean(data_3$mean[data_3$Diagnosis == 0])
m_schizo = mean(data_3$mean[data_3$Diagnosis == 1])

#SD of mean pitch
sd_mean_control = sd(data_3$mean[data_3$Diagnosis == 0])
sd_mean_schizo = sd(data_3$mean[data_3$Diagnosis == 1])

#SD of pitch
sd_control = mean(data_3$sd[data_3$Diagnosis == 0])
sd_schizo = mean(data_3$sd[data_3$Diagnosis == 1])

#SD of SD of pitch
sd_control_sd = sd(data_3$sd[data_3$Diagnosis == 0])
sd_schizo_sd = sd(data_3$sd[data_3$Diagnosis == 1])

#Getting yi and vi
our_study = escalc('SMD', n1i=ss_schizo, n2i=ss_control, m1i=m_schizo, m2i=m_control, sd1i=sd_mean_schizo, sd2i=sd_mean_control, data = data_3)

#make a row to merge with pitch range still need Pitchsd and pitchsdsd for both td and Shcizo (just before yi)
one_row = c('ExpMeth et al. 2017', 2017, ss_schizo, ss_control, m_control, sd_mean_control, m_schizo, sd_mean_schizo, sd_control, sd_schizo, sd_control_sd, sd_schizo_sd, our_study$yi[1], our_study$vi[1])

#Make numeric, then make back into factor further below
#escalc_mean[,1] = as.character(escalc_mean[,1])
#escalc_sd[,1] = as.character(escalc_sd[,1])

#Add the row to PitchRange
escalc_mean2 = rbind(escalc_mean, one_row)
escalc_sd2 = rbind(escalc_sd, one_row)

#make back into factor
#escalc_mean[,1] = as.factor(escalc_mean[,1])
#escalc_sd[,1] = as.factor(escalc_sd[,1])

#Make numeric
escalc_mean2$yi = as.numeric(escalc_mean2$yi)
escalc_mean2$vi = as.numeric(escalc_mean2$vi)
escalc_sd2$yi = as.numeric(escalc_sd2$yi)
escalc_sd2$vi = as.numeric(escalc_sd2$vi)

#------ Do analysis again ------
m2_mean = rma(yi,vi, data= escalc_mean2, slab = Article)
m2_sd = rma(yi,vi, data= escalc_sd2, slab = Article)
forest(m2_mean)
summary(m2_mean)
forest(m2_sd)
summary(m2_sd)

```


3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.

```{r}
# assesing the quality of the litterature (tau and I2)


inf = influence(m2_mean)
print(inf)
plot(inf)
inf2 = influence(m2_sd)
print(inf2)
plot(inf2)

# funnel plot
funnel(m2_mean)
regtest(m2_mean)
ranktest(m2_mean)
funnel(m2_sd)


```

## Tips on the process to follow:

- Download the data on all published articles analyzing pitch schizophrenia: https://www.dropbox.com/s/pmgw8wzc308so1p/Data.csv?dl=0
- Following the procedure in the slides calculate effect size and standard error of the effect size per each study. N.B. we focus on pitch mean and pitch standard deviation.
 . first try using lmer (to connect to what you know of mixed effects models)
 . then use rma() (to get some juicy additional statistics)

- Build a forest plot of the results (forest(model))
 
- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?

- Now look at the output of rma() and check tau and I2
